Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-21 PAPER.tex
Lessons learned papers
Context of PAPER style analysis. For Miguel types.

@@

There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.

>>>>

This paper adds to the growing foundations of lessons which have been documented in  \cite{Patil2016,Jacobs2016} and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.

@@

There are many choices a $21$ cm data analyst must consider, though the space is significantly constrained by 
the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
the sky. However, even within this problem sub-space, questions remain.

 How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
